---
title: "Search and Download"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)

options(tibble.print_min = 6L, tibble.print_max = 6L)
```

## Packages

```{r setup, message=FALSE}
library(tidyverse)
library(ccc)
```

## Search

Use the `ccc_search()` function to look up some cases.

```{r}
results <- ccc_search(
  text = "familia", 
  date_start = "2000-01-01", 
  date_end = "2001-12-31"
)

glimpse(results)
```

This data is a little messy. The `ccc_clean_dataset()` provides some useful tidying, but you might want to consider doing things differently.

```{r}
df <- ccc_clean_dataset(results)
glimpse(df)
```

## Download

Next you'll want to download some texts. You can use either `ccc_txt()` or `ccc_rtf()`. I prefer `ccc_txt()` because it seems most `.rtf` files don't include footnotes.

This is how you download the first ruling:

```{r}
txt <- ccc_txt(df$url[[1]])
```

And this is how you'd download the first 5 rulings:

```{r}
txts <- lapply(df$url[1:5], ccc_txt)
names(txts) <- df$id[1:5]
glimpse(txts)
```

Each text will look something like this:

```{r, results='asis'}
txts[[1]] |> 
  str_trunc(2000) |> 
  cat()
```

## Citations

Finally, you can `extract_citations()` for each individual document as follows:

```{r}
extract_citations(txts[[1]])
```

Or you can do something like this for all documents:

```{r}
lapply(txts, extract_citations)
```
